Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-23 Papers/ms.tex
Get rid of subcaption package
Why the posterior is less crazy for the simulated data

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
%\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{subcaption} % subfigures
\usepackage{float}

@@

\subsection{Reproducibility of the results}\label{sec:convergence}
The ``effective sample size'' returned by DNS, which we have described as the
number of posterior samples, takes into account the fact DNS's target
distribution is not the posterior. However, it does not take autocorrelation
into account, and thus can present an optimistic picture of the accuracy of
any Monte Carlo approximations to posterior quantities. Most standard diagnostic
techniques used in MCMC can be applied here. The simplest of these is a
check of reproducibility. If different runs yield substantially different
results, the MCMC output should be treated with caution. For example, in
Figure~\ref{fig:masses2}, there is a correlation between the mass attributed
to the SIE component and that attributed to substructures. However, the
distribution also appears somewhat ``lumpy'' or multimodal. This is probably
not a feature of the actual posterior distribution, but rather appears due to
imperfect sampling. Whereas a standard Metropolis sampler would move around
very slowly in the hypothesis space, the DNS algorithm naturally spends some
of the time sampling the prior. Therefore, a particle exploring the parameter
space can ``forget'' its good fitting position, move somewhere completely
different, and find another good fitting model in a different location. This
is a natural feature of the algorithm (and is also present in related
algorithms such as parallel tempering). Despite this feature, the patchy
nature of Figure~\ref{fig:masses2} suggests that posterior exploration is
still challenging in this problem.

>>>>

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
%\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{float}

@@

\subsection{Reproducibility of the results}\label{sec:convergence}
The ``effective sample size'' returned by DNS, which we have described as the
number of posterior samples, takes into account the fact DNS's target
distribution is not the posterior. However, it does not take autocorrelation
into account, and thus can present an optimistic picture of the accuracy of
any Monte Carlo approximations to posterior quantities. Most standard diagnostic
techniques used in MCMC can be applied here. The simplest of these is a
check of reproducibility. If different runs yield substantially different
results, the MCMC output should be treated with caution. For example, in
Figure~\ref{fig:masses2}, there is a correlation between the mass attributed
to the SIE component and that attributed to substructures. However, the
distribution also appears somewhat ``lumpy'' or multimodal. This may
not be a feature of the actual posterior distribution, but could arise due to
imperfect sampling. Whereas a standard Metropolis sampler would move around
very slowly in the hypothesis space, the DNS algorithm naturally spends some
of the time sampling the prior. Therefore, a particle exploring the parameter
space can ``forget'' its good fitting position, move somewhere completely
different, and find another good fitting model in a different location. This
is a natural feature of the algorithm (and is also present in related
algorithms such as parallel tempering). Despite this feature, the patchy
nature of Figure~\ref{fig:masses2} suggests that posterior exploration is
still challenging in this problem.

The results for the simulated data (Figure~\ref{fig:masses})
were less complex because of the definite existence of one substructure.
Its mass and position provide some information about the hyperparameters
$\boldsymbol{\alpha}_{\rm lens}$, restricting the probability that
high mass substructures exist far from the image.
